---
title: "PSY8712 Week 8 Project"
author: "Merhar"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducible Image and Online Resources

An image of this project as of *`r format(Sys.Date(), "%d %B %Y")`* can be accessed by clicking [this link](https://mybinder.org/v2/gh/merha013/psy8712-week8/HEAD).

An interactive web app is available by clicking [this link](http://example.com) instead.

## Script Settings and Resources

```{r, echo = TRUE, message = FALSE, warning = FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(rsconnect)
library(shiny)
library(tinytex)
library(tidyverse)
```

## Data Import and Cleaning

The following code uses a single pipeline to create week8_tbl from the data (week3.csv). It converts the timeStart and timeEnd data types into their correct types, calculates each participant’s total number of minutes spent in the study as a new variable called timeSpent, relabels the variables for gender and condition, reverses the code for q5, removes all cases that failed the manipulation check (i.e., the participant responded with anything other than a 1 to q6), and drops q6 from the final tbl. I also created two additional columns called 'average1' and 'average2' that provide the means of q1:q6 and q8:q10 respectively since it is needed in the Visualization section.

```{r, message = FALSE, show_col_types=FALSE}
week8_tbl <- read_csv("../data/week3.csv") %>%
  mutate(timeStart = ymd_hms(timeStart),
         timeEnd = ymd_hms(timeEnd),
         timeSpent = as.numeric(timeEnd-timeStart),
         gender = recode_factor(gender,
                                M = "Male",
                                F = "Female"),
         condition = recode_factor(condition, 
                                   A = "Block A", 
                                   B = "Block B", 
                                   C = "Control"),
         q5 = max(q5)-q5+1,
         average1 = (q1+q2+q3+q4+q5+q6)/6,  # probably a better way to do this, but (q1:q6) wasn't working for me
         average2 = (q8+q9+q10)/3) %>%
  filter(q6==1)
```

## Visualization

The following table shows the data contained in questions 1 through 6. It is paginated so that data is less overwhelming and shows only ten rows at a time.

```{r, echo=FALSE, message=FALSE}
week8_tbl %>%
  select(q1:q6)
```

The following scatterplot was created using the data from week8_tbl and putting the mean scores of questions 1-6 on the x-axis and the mean scores of questions 8-10 on the y-axis. A purple OLS regression line with a shaded error band is included in the depiction. Additionally, the input code to create this scatterplot has been hidden from the final output.

```{r, echo=FALSE, message = FALSE}
week8_tbl %>%
  ggplot(aes(x=average1, y=average2)) +
  geom_point() +
  geom_smooth(method="lm", color="purple") +
  labs(title = "Scatterplot between Mean Scores",
       x = "Mean Scores on Q1-Q6",
       y = "Mean Scores on Q8-Q10")
```

## Analysis

```{r, echo=FALSE, message = FALSE}
(analysis <- cor.test(week8_tbl$average1, week8_tbl$average2))
correlation <- round(analysis$estimate, digits=2) # need to remove the leading 0
```

I observed a correlation of `r correlation` and a p-value of `r analysis$p.value`. This p-value means, using an $\alpha$=0.05, there is at least a `r format(analysis$p.value*100)`% probability of observing the collected data if there were truly no relationship between the mean of questions 1-6 and the mean of questions 8-10. Since `r analysis$p.value` \> $\alpha$, we fail to reject the null hypothesis that the true correlation is equal to 0. There is not enough evidence to conclude that there is a statistically significant relationship between the variables being tested at the 0.05 significance level.

## Data Export

A minimal/skinny version of the dataset appropriate for shiny has been created via a single series of pipes and exported.

```{r}
week8_tbl %>%
  select(timeEnd, gender, condition, average1, average2) %>%
  saveRDS("../shiny/week8/skinny.rds")
```
